Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-10 paper/paper.tex
pass on igor comments

\subsection{Engines}
\label{sec:methodology:engines}~We selected the most popular JS
engines on the web~\Fix{cite} to focus our bug-finding efforts, namely
Microsoft's Chakra~\cite{chakra2018repo}, Google's
v8~\cite{v82018repo}, Mozilla's
SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}.

\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
associated with all \Fix{four} JS engines we analyzed
(section~\ref{sec:methodology:engines}).
\Igor{
  We selected only the seeds that supports integration without external dependencies. 
  In addition, we found in public repositories (ie. GitHub) several kinds of projects 
  that contains javascript files, however, the most of them uses nodejs that have 
  internal functions that our engines does not support. 
  We found a total of four engines projects that we can integrate to our seeds 
  with minor fixes on the files, due the "assertion function" is missing in some cases.
}

Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects.\Mar{identify the sources assoc. with
  the four analyzed engines. you said in the first sentence this is
  one source.}  Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.} It is worth noting that some projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For these projects, we needed to make small changes in the testing
infrastructure to be able to uniformly run tests in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
  que em portugues). isto
  nao deveria levar tempo que justifique escrever wip.}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites
  % \Mar{try to use a single
  %     name (if possible) to facilitate reference in the paper. Use the
  % full path in the URL (citation) to indicate where one can find those
  % files.}
  }
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1031 \\
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

>>>>

\subsection{Engines}
\label{sec:methodology:engines}~We selected the most popular JS
engines on the web~\Fix{ha alguma referencia que de suporte a isto?} to focus our bug-finding efforts, namely
Microsoft's Chakra~\cite{chakra2018repo}, Google's
v8~\cite{v82018repo}, Mozilla's
SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}.

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API\Fix{cite}. We noticed that some of the tests
we found depend on external libraries, which not all engines we use
(see Section~\ref{sec:methodology:engines}) support. We decided to
discard those. For example, many tests we found required a
nodejs\Fix{cite} runtime for execution. Overall, we considered the
test suites of three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines.

\Mar{vc. jah nao fala disto no paragrafo a seguir? se sim, junte os dois.}
We
implemented minor changes on test files with fixable file dependencies. For
example, some of the files used assertion functions defined in their
projects; we replaced those with our definitions.\Mar{not sure if this
  is a good example; why one would like to redefine assertion? why
  didn't you incorporate the assertion function to your infra?}

Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some projects use
distinct frameworks for testing and require external libraries to run
their testing suites. For these projects, we needed to make small
changes in the testing infrastructure to be able to uniformly run
tests in all engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
  que em portugues). isto nao deveria levar tempo que justifique
  escrever wip.}We aimed to use only the JS file with minor fixes to
support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites
  % \Mar{try to use a single
  %     name (if possible) to facilitate reference in the paper. Use the
  % full path in the URL (citation) to indicate where one can find those
  % files.}
  }
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}
